Verifying Demonstrations

### 2018-05-30 paper/SystemModel.tex
Finishes verification part of protocol
This describes Jane (fixes #101).

@@

@@

\begin{definition}[Participation-proof share]
  A \emph{participation-proof share} \(\psh = (\cid, t, l, \pid, \wid)\) is a 
  tuple where:
  \(\cid, t, l\) are as in \cref{DefProtest};
  \(\pid\) is a protester's pseudonym for the protest identified by \(\cid\); 
  and
  \(\wid\) is a witness's pseudonym for a protester with pseudonym \(\pid\).
  We say that \(\psh\) is part of a subprotest \(p = (\cid', t', l')\) iff 
  \(\cid = \cid', t\subseteq t', l\subseteq l'\) and denote this by \(\psh 
    \sqsubseteq p\).
  We let \(\pshs\) be the set of all proof shares.
\end{definition}

@@

\begin{definition}[Participation proof]%
  \label{DefParticipationProof}
  A \emph{participation proof} of protester with pseudonym \(\pid\) 
  participating in a protest \(\prtst = \{ (\cid, t_i, l_i) \}_i\) is the set
  \begin{multline}
    \nonumber
    \prf_{\pid, \prtst} =
    \left\{ \psh = (\cid, t, l, \pid, \wid)\in \pshs \mid
      \exists \sprtst\in \prtst\colon \psh\sqsubseteq \sprtst \right\}
  \end{multline}
  of all proof shares with the same protester and protest identifiers, 
  witnessing time interval \(t\) and location \(l\) is within those of the 
  protest.
  We denote by \(\prfs\) the set of all proofs.
\end{definition}

@@

We can now define the participation count as follows.
\begin{definition}[Participation count]
  We define the \emph{participation count} of a protest \(\prtst\) (as in 
  \cref{DefParticipationProof}) as the cardinality \(|\prfs_{P}^{\str,\theta}|\) 
  of the set of participation proofs \[
    \prfs_{\prtst}^{\str,\theta} = \left\{ \prf_{i,P} \in \prfs \mid
      \str(\prf_{i,j})\geq \theta \right\}
  \] for some strength function \(\str\colon \powerset(\pshs)\to \RR_+\) and a 
  threshold \(\theta\).
\end{definition}
The strength function \(\str\) can be used to regulate trust in witnesses.
One example would be for \(\str\) to return the number of unique witnesses and 
thus let \(\theta\) to be the threshold of the number of required witnesses.
Another example would be to return the number of proof shares issued by trusted 
witnesses and set \(\theta = 1\) to require at least one proof share issued by a 
trusted witness.

>>>>

% cause identifier
\NewVariable{\cid}{cid}

@@

% protest
\NewVariable{\prtst}{P}
% subprotest
\NewVariable{\sprtst}{p}

@@

% proof share
\NewVariable{\psh}{s}
% proof shares
\NewVariable{\pshs}{S}
% protester identifier
\NewVariable{\pid}{pid}
% witness identifier
\NewVariable{\wid}{wid}

\begin{definition}[Participation-proof share]%
  \label{DefProofShare}\label{DefProofShares}
  A \emph{participation-proof share} \(\psh = (\cid, t, l, \pid, \wid)\) is a 
  tuple where:
  \(\cid, t, l\) are as in \cref{DefProtest};
  \(\pid\) is a protester's pseudonym for the protest identified by \(\cid\); 
  and
  \(\wid\) is a witness's pseudonym for a protester with pseudonym \(\pid\).
  We say that \(\psh\) is part of a subprotest \(p = (\cid', t', l')\) iff 
  \(\cid = \cid', t\subseteq t', l\subseteq l'\) and denote this by \(\psh 
    \sqsubseteq p\).
  We let \(\pshs\) be the set of all proof shares.
\end{definition}

@@

% proof
\NewVariable{\prf}{\pi}
% proofs
\NewVariable{\prfs}{\Pi}

\begin{definition}[Participation proof]%
  \label{DefParticipationProof}\label{DefParticipationProofs}
  A \emph{participation proof} of protester with pseudonym \(\pid\) 
  participating in a protest \(\prtst = \{ (\cid, t_i, l_i) \}_i\) is the set
  \begin{multline}
    \nonumber
    \prf_{\pid, \prtst} =
    \left\{ \psh = (\cid, t, l, \pid, \wid)\in \pshs \mid
      \exists \sprtst\in \prtst\colon \psh\sqsubseteq \sprtst \right\}
  \end{multline}
  of all proof shares with the same protester and protest identifiers, 
  witnessing time interval \(t\) and location \(l\) is within those of the 
  protest.
  We denote by \(\prfs\) the set of all proofs.
\end{definition}

@@

We can now define the participation count as follows.
\begin{definition}[Participation count]%
  \label{DefParticipationCount}
  We define the \emph{participation count} of a protest \(\prtst\) (as in 
  \cref{DefParticipationProof}) as the cardinality \(|\prfs_{P}^{\str,\theta}|\) 
  of the set of participation proofs \[
    \prfs_{\prtst}^{\str,\theta} = \left\{ \prf_{i,P} \in \prfs \mid
      \str(\prf_{i,P})\geq \theta \right\}
  \] for some strength function \(\str\colon \powerset(\pshs)\to \RR_+\) and a 
  threshold \(\theta\).
\end{definition}
The strength function \(\str\) can be used to regulate trust in witnesses.
One example would be for \(\str\) to return the number of unique witnesses and 
thus let \(\theta\) to be the threshold of the number of required witnesses.
Another example would be to return the number of proof shares issued by trusted 
witnesses and set \(\theta = 1\) to require at least one proof share issued by a 
trusted witness.

### 2018-05-30 paper/protocol.tex
Minor WIP on verification phase of protocol
Finishes verification part of protocol
This describes Jane (fixes #101).

\dots

>>>>

There are various ways for verifying the participation count, we will cover the 
two suggested just after \cref{DefParticipationCount}.
In the first approach, we do not trust individual witnesses, instead we 
\emph{assume} that it is difficult for Alice to find more than \(\theta\) 
witnesses willing to collude.
Thus we require at least \(\theta\) witnesses to accept a participation proof 
as valid.
In the second approach, we trust certain witnesses but not others.
Thus to accept a participation proof as valid, we require at least one trusted 
witness.

\paragraph{Without trusted witnesses}

To verify the participation count for a protest \(P = (\cid, t, l)\) (see 
\cref{DefProtest}), a verifier must download all the proof shares \(\psh_i = 
  (\cid, \pid_i, \wid_i, t_s^{(i)}, t_s^{\prime (i)}, t_e^{(i)}, t_e^{\prime 
    (i)}, l_i, \prf_{\pid_i}, \prf_{\wid_i})\), from the blockchain and verify 
\(\prf_{\pid_i}\) and \(\prf_{\wid_i}\) and that the interval starting at the 
latest of \(t_s^{(i)}, t_s^{\prime (i)}\) and ending at the earliest of 
\(t_e^{(i)}, t_e^{\prime (i)}\) is a subset of \(t\) and that \(l_i\subseteq 
  l\).
Any proof share that does not verify correctly will be discarded.
At this point, the verifier has constructed the set \(S\) from 
\cref{DefProofShares} and can thus construct any participation proof 
\(\prf_{\pid_i, P}\) as in \cref{DefParticipationProof}.

Now, we simply define \(\str[\prf_{\pid_i, P}] = |\prf_{\pid_i, P}|\) and then 
the verifier can compute the participation count \(|\prfs_P^{\str, \theta}|\) 
as in \cref{DefParticipationCount}.

\paragraph{With trusted witnesses}

For the this approach, we must adapt the selection of proof shares from the 
blockchain by selecting only proof shares issued by witnesses that the verifier 
trusts.
Thus the verifier must be able to recognize proof shares issued by trusted 
witnesses, but as \(\prf_\wid\) is currently constructed, this is not possible.
So trusted witnesses must complement their proofs by a digital signature that 
the verifier can recognize.

When \(S\) only contains proof shares issued by witnesses the verifier trusts, 
we let \(\str[\prf_{\pid_i, P}] = 1\) and let \(\theta = 1\).
Then the verifier can compute the participation count \(|\prfs_P^{\str, 
    \theta}|\) as in \cref{DefParticipationCount}.
